Very simplified likelihood

### 2024-03-01 inst/very_simplified_likelihood.Rmd
sensible park run null

---
title: "Very simplified likelihood"
author: "Robin Hankin"
output: html_document
---

@@

```{r testran,cache=FALSE}
runif(10)
```

@@

```{r optimize_insilicco,cache=TRUE}
optim(par=c(4,-6),likeinsilico,control=list(fnscale= -1),M=M)
```

```{r makeZcontourdataset,cache=TRUE}
a <- seq(from=3.8,to=4.2,by=0.1)
b <- seq(from=-6.1,to=-5.6,by=0.1)
Z <- as.matrix(expand.grid(a,b))
Z <- apply(Z,1,function(x){likeinsilico(x,M=M)})
Z <- matrix(Z,length(a),length(b))
```

```{r doZcontour}
Z <- Z-max(Z)
contour(a,b,Z,levels=-c(0:10,15,20,30))
points(alpha_true,beta_true,pch=16,cex=4)
grid()
persp(a,b,Z)
```

@@

```{r definelikelihood}

L <- function(a,results){
   out <- a*0
   for(i in seq_len(nrow(results))){
   jj <- f_vec_a(a,r=results$place[i]-1,results$runners[i]-1,log=TRUE)
   out <- out + jj
   }
   out[is.infinite(out)] <- NA
   return(out)
}
```

@@

```{r plotlike}
plot(a,La,ylab='support')
abline(h=c(0,-2))
```

```{r optimsinglelike}
optimize(function(a){L(a,results)},c(0.2,0.4),maximum=TRUE)
```

>>>>

---
title: "Very simplified likelihood"
author: "Robin Hankin"
output: bookdown::html_document2
---

@@

@@

```{r optimize_insilicco,cache=TRUE}
optim_ab <- optim(par=c(4,-6),likeinsilico,control=list(fnscale= -1),M=M)
optim_ab
```

```{r makeZcontourdataset,cache=TRUE}
a <- seq(from=3.8,to=4.2,by=0.01)
b <- seq(from=-6.4,to=-5.6,by=0.01)
Z <- as.matrix(expand.grid(a,b))
Z <- apply(Z,1,function(x){likeinsilico(x,M=M)})
Z <- matrix(Z,length(a),length(b))
```

```{r doZcontour}
Z <- Z-max(Z)
Z <- pmax(Z,-10)
contour(a,b,Z,levels=-c(0:10,15,20,30))
points(alpha_true,beta_true,pch=16,cex=4)
jj <- optim_ab$par
points(jj[1],jj[2],pch=4,cex=4,col='red')
grid()
persp(a,b,Z)
```

@@

```{r definesupportparkrun}
L <- function(a,results){
   out <- a*0
   for(i in seq_len(nrow(results))){
   jj <- f_vec_a(a,r=results$place[i]-1,results$runners[i]-1,log=TRUE)
   out <- out + jj
   }
   out[is.infinite(out)] <- NA
   return(out)
}
```

@@

```{r optimsinglelike}
(optparkrun <- optimize(function(a){L(a,results)},c(0.2,0.8),maximum=TRUE))
f <- function(a){L(a,results)-2}
```

```{r plotparkrunlike, fig.cap="Support curve for author's generalized Bradley-Terry strength.  Evaluate of $\\hat{a}\\simeq 0.448$ has a support of zero"}
plot(a,La,xlab="generalized Bradley-Terry strength",ylab="support")
abline(h=c(0,-2))
abline(v=0.5)
```

Figure \@ref(fig:plotparkrunlike) shows a support curve for the
author's generalized Bradley-Terry strength, normalized so that
$\mathcal{S}(\hat{a})=0$.  We see a credible interval [that is, values
of $a$ for which $\mathcal{S}(a)\geqslant -2$] of about
